---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gdalwebsrv

<!-- badges: start -->
<!-- badges: end -->

The goal of gdalwebsrv is to provide access to some online image servers using standard tools. 

This package contains no code for *reading rasters*, it's simply a convenient way to access *configuration files* that can be used as sources of web imagery. 



WIP, currently pretty limited there are only 5 sources (from 17 ) that we allow in for now while things are figured out. 

## Installation


``` r
remotes::install_github("hypertidy/gdalwebsrv")
```


You can install the released version of gdalwebsrv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gdalwebsrv")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gdalwebsrv)

available_sources()

srcfile <- server_file("wms_googlemaps_tms")

library(gdalio)
g <- gdalio_graphics(srcfile)
plot(g)

gdalio_set_default_grid(list(extent = c(-1, 1, -1, 1) * 1e6, 
                            dimension = c(1024, 1024), 
                            projection = "+proj=laea +lon_0=147 +lat_0=-42"))
l <- gdalio_graphics(srcfile)
plot(l)

```


## Code of Conduct
  
Please note that the gdalwebsrv project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
