---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gdalwebsrv

<!-- badges: start -->
<!-- badges: end -->

The goal of gdalwebsrv is to provide access to some online image servers using standard tools. 

This package contains no code for *reading rasters*, it's simply a convenient way to access *configuration files* that can be used as sources of web imagery. 



WIP, currently pretty limited there are only 5 sources (from 17 ) that we allow in for now while things are figured out. 

## Installation


``` r
remotes::install_github("hypertidy/gdalwebsrv")
```


You can install the released version of gdalwebsrv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gdalwebsrv")
```

## Example

This is a basic example to get various kinds of imagery. 

Each `server_file()` is a path to a GDAL readable tile server, one of each of the `available_sources()`. 

```{r example}
library(gdalwebsrv)

available_sources()

## all this package does is keep a list of these 
gmap_file <- server_file("wms_googlemaps_tms")
```


Now we might use the server one way or another. 

```{r read}
library(gdalio)
g <- gdalio_graphics(gmap_file)
plot(g)

gdalio_set_default_grid(list(extent = c(-1, 1, -1, 1) * 1e6, 
                            dimension = c(1024, 1024), 
                            projection = "+proj=laea +lon_0=147 +lat_0=-42"))
gmap <- gdalio_graphics(gmap_file)
plot(gmap)

vmap <- gdalio_graphics(server_file("wms_virtualearth"))
plot(vmap)

temap <-  gdalio_graphics(server_file("wms_googlemaps_terrainextra_tms"))
plot(temap)

omap <- gdalio_graphics(server_file("wms_openstreetmap_tms"))
plot(omap)

```

Something different. 

```{r longlat}
gdalio_set_default_grid(list(extent = c(-120, -10, -50, 50), 
                            dimension = c(768, 512)/1.5, 
                            projection = "+proj=longlat"))

lerc <-  gdalio_matrix(server_file("wms_arcgis_terrain_tms_lerc"), bands = 1)
image(seq(-120, -10, length.out = nrow(lerc) + 1), 
          seq(-50, 50, length.out = ncol(lerc) + 1), lerc)
maps::map(add = TRUE)
```

## Code of Conduct
  
Please note that the gdalwebsrv project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
