---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gdalwebsrv

<!-- badges: start -->
<!-- badges: end -->

The goal of gdalwebsrv is to provide access to some online image servers using standard tools. 

This package contains no code for *reading rasters*, it's simply a convenient way to access *configuration files* that can be used as sources of web imagery. 



WIP, currently pretty limited there are only 5 sources (from 17 ) that we allow in for now while things are figured out. 

## Installation


``` r
remotes::install_github("hypertidy/gdalwebsrv")
```


You can install the released version of gdalwebsrv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gdalwebsrv")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gdalwebsrv)

available_sources()

srcfile <- server_file("wms_virtualearth")

raster::brick(srcfile)

stars::read_stars(srcfile, proxy = TRUE)

ex <- c(xmin = 1e7, xmax = 2e7, ymin = -6e6, -1e6)

## not sure how to *read* sensibly from those yet so rely on lazyraster for now
  library(lazyraster)
  lr <- lazyraster(srcfile)

  cr <- crop(lr, ex)
  rr <- raster::brick(as_raster(cr, band = 1), 
              as_raster(cr, band = 2), 
            as_raster(cr, band = 3))

  
  library(raster)
plotRGB(rr)


read_ex <- function(name, ex) {
  library(lazyraster)
  srcfile <- server_file(name)
  lr <- lazyraster(srcfile)

  cr <- crop(lr, ex)
  rr <- raster::brick(as_raster(cr, band = 1), 
              as_raster(cr, band = 2), 
            as_raster(cr, band = 3))

  rr
}
srcs <- available_sources()
for (i in seq_along(srcs)) {
  plotRGB(read_ex(srcs[i], ex))
  text(ex[2] - 1.5e6, ex[4] - 1e6, lab = srcs[i], col = "white")
}


```


## Code of Conduct
  
Please note that the gdalwebsrv project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
